Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-14 paper/manuscript.Rmd
update Q3

3) Does reproductive status (presence of a calf-at-heel) or demographic class
(age, sex) influence propensity for oceanic swimming? Our initial observation
was of an adult male, but all collared individuals were adult females. Are
younger caribou more likely to swim due to heightened competition? Are males
more likely to swim in the summer given the are not restricted based on presence
of a calf-at-heel, as females are.

>>>>

3) Does reproductive status (presence of a calf-at-heel) or demographic class
(age or sex) influence propensity for oceanic swimming? Our initial observation
was of an adult male, but all collared individuals were adult females. Are
younger caribou more likely to swim due to heightened competition? Are males or
females without a calf-at-heel more likely to swim in the summer given the are
not restricted based on presence of a calf-at-heel, as females are.
